### 2021-02-20 README.Rmd
Add hex logo.
Edit the README file.

# yowie

@@

The goal of yowie is to provide longitudinal wages data sets along with several demographic variables from The National Longitudinal Survey of Youth (NLSY) from survey year 1979 to 2018. There are three data sets in this package:

>>>>

# yowie <a href='https://numbats.github.io/yowie/'><img src='man/figures/logo.png' align="right" height="138.5" /></a>

@@

The goal of `yowie` is to provide longitudinal wages data sets along with several demographic variables of Americans from [the National Longitudinal Survey of Youth (NLSY79)](https://www.nlsinfo.org/content/cohorts/nlsy79) from Round 1 (the survey year 1979) to Round 28 (the survey year 2018). The NLSY79 is a longitudinal project held by the U.S. Bureau of Labor Statistics that follows the lives of a sample of American youth born between 1957-64. The cohort originally included 12,686 respondents ages 14-22 when first interviewed in 1979. There are three data sets provided in this package:
